---
title: "Internal Assessment 1"
author: "Makeup Test"
output: pdf_document
---

\begin{center}
{\Large ECON03SEC1}\\
{\Large Department of Economics}\\
{\Large Presidency University, Kolkata}\\
{\large Full Marks: 30}\\
{\large 14/12/2022}
\end{center}


Answer the following questions: [$6 \times 5 = 30$]


1. Explain the following codes and their outputs.
```{r, eval=FALSE}
a2 <- matrix(1:9, nrow = 3)
colnames(a2) <- c("A", "B", "C")

a2[c(TRUE, FALSE, TRUE), c("B", "A")]
```


2. Using the `midwest` dataset in the `ggplot2` package, replicate the following plot.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
options(scipen = 999)
library(tidyverse)
data(midwest)
midwest %>% 
  filter(poptotal >= 0 & poptotal <= 500000) %>% 
ggplot()+
  geom_point(aes(x = area,
                 y = poptotal,
                 col = state,
                 size = popdensity), 
             alpha = 0.5)
```

3. Tidy and replicate the `fish_encounters` dataset in the `tidyr` package as given below.

```{r, echo=FALSE}
fish_encounters %>% 
  pivot_wider(names_from = station,
              values_from = seen) %>% 
  na.omit()  
```

4. Which specie has the longest and widest petal in the `iris` dataset in the base R `datasets` packages?
```{r, echo=FALSE, eval=FALSE}
iris %>% 
  group_by(Species) %>% 
  summarise(max(Petal.Length), max(Petal.Width))
```

5. How many and which species have sepal length longer than their mean value.
```{r}
iris %>% 
  filter(Sepal.Length > mean(Sepal.Length)) %>% 
  group_by(Species) %>% 
  summarise(`Sepal.Length > mean(Sepal.Length)` = n())
```

6. Which specie has the highest difference in their petal width.
```{r}
iris %>% 
  group_by(Species) %>% 
  summarise(sd = sd(Petal.Width))
```

