---
title: "Internal Assessment 1"
author: "Series 1"
output: pdf_document
---


\begin{center}
{\Large ECON03SEC1}\\
{\Large Department of Economics}\\
{\Large Presidency University, Kolkata}\\
{\large Full Marks: 30}\\
{\large 09/11/2022}
\end{center}


Answer the following questions: [$6 \times 5 = 30$]

1. Run the following codes and explain why the value of `address1` is shown as `NA` while the `class(address1)` is `numeric`?
```{r, eval=FALSE}
x1 <- "Presidency"
x2 <- "University"
x3 <- "Kolkata"
address <- c(x1, x2, x3)
address1 <- as.numeric(address)
address1
class(address1)
```

2.Using the `iris` dataset in the base R `datasets` package, replicate the following plot.

```{r, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%"}
library(tidyverse)
ggplot(iris)+
  geom_point(aes(x = Sepal.Length,
                 y = Sepal.Width,
                 shape = Species
                 ),
             col = "red")+
  facet_wrap(Species ~ .)
```

3. Tidy and replicate the `us_rent_income` dataset in the `tidyr` package as given below.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
us_rent_income %>% 
  pivot_wider(names_from = variable,
              values_from = estimate) %>% 
  filter(moe <= 3) %>% 
  arrange(rent)

```

4. Calculate the mean *mpg* (miles per gallon) of the  cars with 6 and 4 cylinders in `mtcars` dataset in the base R `datasets` package.
```{r, echo=FALSE, eval=FALSE}
mtcars %>% 
  select(mpg,cyl) %>% 
  filter(cyl %in% c(6,4)) %>%
  group_by(cyl) %>% 
  summarise(mean(mpg))
```

5. Which type of transmission (manual or automatic) has a higher variation (standard deviation) of *mpg* in the `mtcars` dataset in the base R `datasets` package?

```{r, echo=FALSE, eval=FALSE}
mtcars %>% 
  select(mpg, am) %>% 
  group_by(am) %>% 
  summarise(sd(mpg))
  
```

6. What is the average displacement of a manual car with 4 cylinders in the `mtcars` dataset in the base R `datasets` package?
```{r, echo=FALSE, eval=FALSE}
mtcars %>% 
  filter(cyl == 4 & am == 1) %>% 
  summarise(mean(disp))
```