---
title: "Internal Assessment 1"
author: "Series 2"
output: pdf_document
---

\begin{center}
{\Large ECON03SEC1}\\
{\Large Department of Economics}\\
{\Large Presidency University, Kolkata}\\
{\large Full Marks: 30}\\
{\large 09/11/2022}
\end{center}


Answer the following questions: [$6 \times 5 = 30$]

1. Explain the following codes and their outputs.
```{r, eval=FALSE}
a1 <- 12; class(a1); length(a1)
names(a1) <- 'Number'; names(a1)
```

2. Using the `mpg` dataset in the `ggplot2` package, replicate the following plot.

```{r, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%"}
library(tidyverse)
na.omit(mpg) %>% 
ggplot(aes(manufacturer, displ))+
  geom_bar(aes(fill = class),
           stat = "identity")+
  coord_flip()
```

3. Tidy and replicate the `us_rent_income` dataset in the `tidyr` package as given below.

```{r, echo=FALSE}
us_rent_income %>% 
  pivot_wider(names_from = variable,
              values_from = estimate) %>% 
  filter(moe <= 3) %>% 
  arrange(rent)

```

4. Which species have blue eyes in the `starwars` dataset in the `dplyr` package?
```{r, echo=FALSE, eval=FALSE}
starwars %>% 
  filter( eye_color == "blue") %>% 
  group_by(species) %>% 
  count()
```

5. How many female humans are there in the `starwars` dataset in the `dplyr` package ?
```{r, echo=FALSE, eval=FALSE}
starwars %>% 
  filter(species == "Human" & sex == "female") %>% 
  select(species, sex) %>% 
  count()
```

6. In the `starwars` dataset in the `dplyr` package, which species has the most number of blue eye colour?
```{r, echo=FALSE, eval=FALSE}
starwars %>% 
  filter(eye_color== "blue") %>% 
  group_by(species) %>% 
  count()
```