---
title: "Internal Assessment 1"
output: pdf_document
---

\begin{center}
{\Large ECON03SEC1 (Backlog)}\\
{\Large Department of Economics}\\
{\Large Presidency University, Kolkata}\\
{\large Full Marks: 50}\\
{\large 23 Nov 2023}
\end{center}

## `ggplot2` 
## Answer any 2 questions. [2 x 2.5 = 5]

1. Using the `mpg`dataset in the `ggplot2` package, replicate the following plot.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
ggplot(mpg)+
  geom_histogram(aes(hwy, fill = drv),
                 alpha = 0.5)+
  facet_grid(drv ~ .)
```

2. Using the `midwest` dataset in the `ggplot2` package, replicate the following plot.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
options(scipen = 999)
data(midwest)
midwest %>% 
  filter(poptotal >= 0 & poptotal <= 500000) %>% 
ggplot()+
  geom_point(aes(x = area,
                 y = poptotal,
                 col = state,
                 size = popdensity), 
             alpha = 0.5)
```

3. Using the `iris` dataset in the base R `datasets` package, replicate the following plot.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(iris)+
  geom_point(aes(x = Sepal.Length,
                 y = Sepal.Width,
                 shape = Species,
                 col = Species))
```

4. Using the `iris` dataset in the base R `datasets` package, replicate the following plot.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(iris)+
  geom_point(aes(x = Sepal.Length,
                 y = Sepal.Width,
                 shape = Species
                 ),
             col = "red")+
  facet_wrap(Species ~ .)
```




## `dplyr`
## Answer any 3 questions. [ 3 $\times$ 5 = 15]
5. Which species have blue eyes in the `starwars` dataset in the `dplyr` package?
```{r, echo=FALSE, eval=FALSE}
starwars %>% 
  filter( eye_color == "blue") %>% 
  group_by(species) %>% 
  count()
```

6. How many female humans are there in the `starwars` dataset in the `dplyr` package ?
```{r, echo=FALSE, eval=FALSE}
starwars %>% 
  filter(species == "Human" & sex == "female") %>% 
  select(species, sex) %>% 
  count()
```


7. In the `starwars` dataset in the `dplyr` package, what is the average mass of female Human species ?
```{r, echo=FALSE, eval=FALSE}
starwars %>% 
  filter(species == "Human" & sex == "female") %>% 
  summarise(mean_mass = mean(na.omit(mass)))
```

8. In the `starwars` dataset in the `dplyr` package, how many species have a fair skin colour?
```{r, echo=FALSE, eval=FALSE}
starwars %>% 
  filter(skin_color == "fair") %>% 
  select(species, skin_color)
```


## `tidyr`
## Answer any 3 questions. [ 3 $\times$ 5 = 15]

9. Tidy and replicate the `fish_encounters` dataset in the `tidyr` package as given below.

```{r, echo=FALSE}
fish_encounters %>% 
  pivot_wider(names_from = station,
              values_from = seen) %>% 
  na.omit()  
```

10. Tidy and replicate the `who` dataset in the `tidyr` package as given below.
```{r, echo=FALSE}
who %>% 
  pivot_longer(cols = new_sp_m014:newrel_f65,
               names_to = "Diagnosis",
               values_to = "Value") %>% 
  filter(country == "India" & year == 2002) %>% 
  arrange(desc(Value))
```

11. Tidy and replicate the `world_bank_pop` dataset in the `tidyr` package as given below.

```{r, echo=FALSE}
world_bank_pop %>% 
  pivot_longer(cols = `2000`: `2017`,
               names_to = "Year",
               values_to = "Population") %>% 
  filter(country == "IND" & Year == 2000) %>% 
  arrange(Population)
```

12. Tidy and replicate the `population` dataset in the `tidyr` package as given below.

```{r, echo=FALSE}
population %>% 
  pivot_wider(names_from = year,
              values_from = population) %>% 
  filter(country %in% c("India", "China")) %>% 
  arrange(desc(country))
```



## base R
## Answer any 3 questions. [ 3 $\times$ 5 = 15]

13. Explain the following codes and their outputs.
```{r, eval=FALSE}
a1 <- 12; class(a1); length(a1)
names(a1) <- 'Number'; names(a1)
```

14. Explain the following codes and their outputs.
```{r, eval=FALSE}
a2 <- matrix(1:9, nrow = 3)
colnames(a2) <- c("A", "B", "C")

a2[c(TRUE, FALSE, TRUE), c("B", "A")]
```

15. Explain the following codes and their outputs.
```{r, eval=FALSE}
month_levels <- c(
  "Jan", "Feb", "Mar", "Apr", "May", "Jun", 
  "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"
)
a4 <- factor(c("Dec", "Apr", "Jan", "Mar"), levels = month_levels)
a4
```

16. Explain the following codes and their outputs.
```{r, eval=FALSE}
a5 <- factor(c("high", "low", "medium", "medium", "high"), 
             levels = c("low", "medium", "high"), ordered = TRUE)
a5
```


