---
title: "Sample Questions"
date: "2023-11-01"
output: html_document
---

## ggplot2

1. Using the `mpg` dataset in the `ggplot2` package, replicate the following plot.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
```

## dplyr

2. In the `starwars` dataset in the `dplyr` package, which species has the most number of blue eye colour?
```{r, echo=FALSE, eval=FALSE}
starwars %>% 
  filter(eye_color== "blue") %>% 
  group_by(species) %>% 
  count()
```

## tidyr

3. Tidy and replicate the `construction` dataset in the `tidyr` package as given below. 

```{r, echo=FALSE}
construction %>% 
  pivot_longer(cols = Northeast:West, 
               names_to = "Region",
               values_to = "Completed_Units_Region") %>% 
  pivot_longer(cols = `1 unit`: `5 units or more`,
               names_to = "Size",
               values_to = "Completed_Units_Size")
```

## base R
4. Run the following codes and explain why the value of `address1` is shown as `NA` while the `class(address1)` is `numeric`?
```{r, eval=FALSE}
x1 <- "Presidency"
x2 <- "University"
x3 <- "Kolkata"
address <- c(x1, x2, x3)
address1 <- as.numeric(address)
address1
class(address1)
```
