---
title: "Internal Assessment 2"
output:
  pdf_document: default
  editor_options:
  chunk_output_type: console
---

\begin{center}
{\Large ECON03SEC1}\\
{\Large Department of Economics}\\
{\Large Presidency University, Kolkata}\\
{\large Full Marks: 40}\\
{\large 21/01/2022}
\end{center}





\begin{center}
\textbf{Group 1 (R)}
\end{center}

Answer all of the following questions. [4 $\times$ 5 = 20]

1. Which species have blue eyes in the `starwars` dataset in the `dplyr` package? 
```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
starwars %>% 
  filter( eye_color == "blue") %>% 
  group_by(species) %>% 
  count()
```

2. Tidy and replicate the `construction` dataset in the `tidyr` package as given below. 

```{r,  echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
construction %>% 
  pivot_longer(cols = Northeast:West, 
               names_to = "Region",
               values_to = "Completed_Units_Region") %>% 
  pivot_longer(cols = `1 unit`: `5 units or more`,
               names_to = "Size",
               values_to = "Completed_Units_Size")
```

3. Run the following codes and explain why the value of `address1` is shown as `NA` while the `class(address1)` is `numeric`?
```{r, eval=FALSE}
x1 <- "Presidency"
x2 <- "University"
x3 <- "Kolkata"
address <- c(x1, x2, x3)
address1 <- as.numeric(address)
address1
class(address1)
```

4. Using the `mpg`dataset in the `ggplot2` package, replicate the following plot.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
ggplot(mpg)+
  geom_histogram(aes(hwy, fill = drv),
                 alpha = 0.5)+
  facet_grid(drv ~ .)
```



\begin{center}
\textbf{Group 2 (Excel)}
\end{center}

Answer all of the following questions. [4 $\times$ 5 = 20]

1. Using the data `GDP.xlsx`, for any two countries plot separate line charts for the components of GDP (Household Consumption Expenditure, Government final consumption expenditure, Net exports and Gross Capital formation).
2. Which specie has the longest and the widest petal in the `iris.xlsx` data?
3. How many years of data are available for each country in the `GDP.xlsx` dataset? How many countries do not have data for all the years?
4. Suppose that the firm’s production function is $Q=F(K,L)=50K^{0.5}L^{0.5}$. Suppose, too, that the price of labour w=5 and the price of capital r=20. What is the cost minimising input bundle if the firm wants to produce 1,000 units per year?
